Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-06 CVPR16/Source/contBBoxModel.tex
Parameter settings, Cite related work by Reviewer 2

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of our proposed detection bounding box is known to be
occluded, we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundaries of the detection bounding box, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in the detection score is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix as follows
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

>>>>

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ as described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of our proposed detection bounding box is known to be
occluded, we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundaries of the detection bounding box, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in the detection score is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix as follows
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

### 2016-04-06 CVPR16/Source/discussions.tex
Parameter settings, Cite related work by Reviewer 2

We have presented a continuous model for occlusion modeling in 3D. A key advantage is its physically-inspired modeling that lends flexibility towards occlusion reasoning for various elements of scene understanding, such as point tracks, object detection bounding boxes and scores. We demonstrate unified modeling for different applications such as point tracks associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.

>>>>

We have presented a theoretically novel continuous model for occlusion reasoning in 3D. A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores. We demonstrate unified modeling for different applications such as point tracks associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference. Another direction for future work is to replace a single ellipsoid by a set of spheres for modelling a translucent object~\cite{Rhodin2015}, which will better capture object boundary and appearance while remaining a continuous model.
